Summary Tables

### 2021-07-15 summary_tables.Rmd
Get propensities from get_scenario_settings instead

|accra|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.5|47.4|63.1 |

|bangalore|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.3|2.6|0.1 |
| cycle | 3.3|10.1|0.6 |
| car | 0.2|5.3|6.6 |
| motorcycle | 1.0|35.4|60.9 |
| bus | 4.4|40.2|29.7 |

|belo_horizonte|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.1|8.6|0.3 |
| cycle | 1.6|2.7|0.2 |
| car | 7.3|65.1|43.9 |
| motorcycle | 1.3|10.1|5.0 |
| bus | 0.4|11.0|43.5 |

|bogota|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.8|12.0|2.0 |
| car | 1.5|26.6|29.2 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.6|56.7 |

|buenos_aires|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 80.1|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.4|21.2 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|51.0|75.9 |

|cape_town|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|5.3|1.9 |
| cycle | 0.2|0.5|0.1 |
| car | 8.0|55.5|48.1 |
| motorcycle | 0.0|0.7|0.4 |
| bus | 7.5|37.9|49.0 |

|delhi|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.4|10.1|0.9 |
| cycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.8|25.0|40.9 |

|mexico_city|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.4|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.8|35.3|64.7 |

|santiago|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.6|21.8|64.6 |

|sao_paulo|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 82.6|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.2|36.8 |
| motorcycle | 0.8|3.1|1.9 |
| bus | 1.0|22.0|59.7 |

|vizag|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 86.1|19.6|0.1 |
| cycle | 2.6|6.6|2.0 |
| car | 0.6|2.4|2.8 |
| motorcycle | 6.9|24.1|24.3 |
| bus | 0.8|26.7|54.8 |

>>>>

## Case study specific propensities
```{r message=F, error=F, warning=FALSE}
get_scen_settings <- ithimr::get_scenario_settings()
